---
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  fig.path = "man/figures/README-"
)
```


# smnet


[![CRAN status](https://www.r-pkg.org/badges/version/smnet)](https://cran.r-project.org/package=smnet)
[![](https://cranlogs.r-pkg.org/badges/smnet)](https://cran.r-project.org/package=smnet)
[![cran checks](https://cranchecks.info/badges/summary/smnet)](https://cran.r-project.org/web/checks/check_results_smnet.html)  


Overview
---

Fits flexible additive models to data on stream networks, taking account of flow-connectivity of the network.  Models are fitted using penalised least squares.


Installation 
---

To install the development version of the package, use
```{r, eval = FALSE}
remotes::install_github("alastairrushworth/smnet")
```

To install the CRAN version of the package, use
```{r, eval = FALSE}
install.packages("smnet")
```

References
---

O’Donnell, D., Rushworth, A., Bowman, AW., Scott, EM., Hallard, M. (2014). [Flexible regression models over river networks.](https://alastairrushworth.github.io/papers/flexible_regression_river_networks.pdf) Journal of the Royal Statistical Society: Series C (Applied Statistics). 63 (1), 47-63.

